
```{r Libraries}
library(MASS)
library(tidyverse)
library(plotly)
library(ggalt)
library(vegan)
```

```{r}
#We have 34 'variables'
#Multi-Dimensional Scaling
#Reducing from 34 Dimensions to k=2 dimensions

#Classical MultiDimensional Scaling - CMD or Metric MultiDimensional Scaling (MDS)

mdsPowerDist<-cmdscale(powerDist,k=2,eig=TRUE)
```


```{r Import Data}
AcornInfo<-read_csv("AcornInfo-1.csv")
comfortable<-read_csv("comfortable.csv")
pd<-load("powerDist.RData")
```

Q1. Create a metric multdimensional scaling. Plot using symbols/colors to represent Tariff and Group (the 3-level variable aggregating the acorn categories). Make a second plot showing total use as bubble size, using color to represent Group. Summarize any trends or interesting features in these two plots.


```{r Q1}
#Multi-Dimensional Scaling
mdsPowerDist<-cmdscale(powerDist,k=2,eig=TRUE)

mdsPowerDist.df<-data.frame(mdsPowerDist$points)%>%
                    select(Y1=X1,Y2=X2)

mdsPowerDist.df$Tariff_Group <- rownames(mdsPowerDist.df)

mdsPowerDist.df$Tariff<-rownames(mdsPowerDist.df)%>%word(2)

mdsPowerDist.df$ACornCategory<-word(rownames(mdsPowerDist.df,1))

#Join with AcornInfo
mdsPowerDist.df<-inner_join(x=mdsPowerDist.df,AcornInfo%>%select(Acorn,Group,TotalUse),by=c("ACornCategory"="Acorn"))

```

```{r}
p<-mdsPowerDist.df%>%
  ggplot(aes(x=Y1,y=Y2,color=Group,shape=Tariff))+
  geom_point()+
  scale_color_manual(values=c("#66FF33","#FF3333","#CC00CC"))+
  labs(title="Principal Coordinates using pairwise distances of electricity consumption")
  
ggplotly(p)

```

```{r Bubble Plot}
#Total Use as Bubble Size
p<-mdsPowerDist.df%>%
  mutate(TotalUse=round(TotalUse,4))%>%
  ggplot(aes(x=Y1,y=Y2,color=Group,label=ACornCategory))+
  geom_point(shape=1,fill="grey",aes(size=TotalUse))+
  scale_size_continuous(range=c(10,40),trans="exp")+
  labs(title="Bubble Plot")

ggplotly(p)
```
```{r}
colors=AcornInfo$Group

colors[colors=="Affluent"]="Green"
colors[colors=="Comfortable"]="Blue"
colors[colors=="Adversity"]="Red"
colors
symbols(mdsPowerDist$points,circles=AcornInfo$TotalUse,fg=colors,
        main="Principal Coordinates of pairwise distances by Group sized by Total Use")
colors
```


Q2. Create a dendrogram using complete linkage. Plot the dendrogram, labeling the leaves with the category they represent. Cut the dendrogram so four groups are created–show this on the plot. Make a table of these four groups and the three aggregated socio economic groups, and a separate table of the dendrogram groups and electricity tariff types. Are the dendrogram groups associated with either the socio economic group or tariff? Do not perform a test, but summarize any trends in your tables.

```{r}
mod<-hclust(powerDist)
plot(mod,hang=-1,xlab="Group",sub="",labels=as.factor(AcornInfo$Group))
rect.hclust(mod,k=4)


#Cut the dendrogram into k=4 groups
table1<-table(cutree(mod,k=4),AcornInfo$Group)
```

```{r Association with Acorn Group}

table1_melt<-table1%>%
  as.data.frame()%>%
  mutate(Dendrogram_Group =Var1,
         ACornGroup = Var2)

p<-table1_melt%>%
  ggplot(aes(x=Dendrogram_Group,y=Freq,label=Freq))+
  geom_bar(stat="Identity",aes(fill=ACornGroup))+
  coord_flip()+
  labs(title="ACorn group by Dendrogram Group")+
  xlab("Dendrogram Group")+
  ylab("Count")
ggplotly(p)

table2<-table(cutree(mod,k=4),AcornInfo$Tariff)
```


```{r Association with Tariff Group}
table2_melt<-table2%>%
  as.data.frame()%>%
  mutate(Dendrogram_Group=Var1,
         Tariff=Var2)

p<-table2_melt%>%
  ggplot(aes(x=Dendrogram_Group,y=Freq))+
  geom_bar(stat="Identity",aes(fill=Tariff))+
  coord_flip()+
  labs(title="Tariff Group by Dendrogram Group")+
  xlab("Dendrogram Group")+
  ylab("Count")

ggplotly(p)

```

```{r Visualise the Clusters}

Clustered<-mdsPowerDist.df%>%
  inner_join(data.frame(Dendrogram_Group=cutree(mod,k=4),
                        Tariff_Group=names(cutree(mod,k=4))),
             by=c("Tariff_Group"="Tariff_Group"))


options(scipen = 999)
p<-Clustered%>%
  ggplot(aes(x=Y1,y=Y2))+
  geom_point(aes(color=Group,shape=Tariff))+
    scale_color_manual(values=c("#66FF33","#FF3333","#CC00CC"))+
  geom_encircle(aes(group=as.factor(Dendrogram_Group)),color="red",expand=0.02)+
  labs(title="Principal Coordinates with Hierarchical Clustering (Complete linkage, height 4)")

p
```
