
```{r Libraries}
library(MASS)
library(tidyverse)
library(plotly)
library(ggalt)
library(vegan)
```




```{r Import Data}
AcornInfo<-read_csv("AcornInfo-1.csv")
comfortable<-read_csv("comfortable.csv")
pd<-load("powerDist.RData")
```

Q1. Create a metric multdimensional scaling. Plot using symbols/colors to represent Tariff and Group (the 3-level variable aggregating the acorn categories). Make a second plot showing total use as bubble size, using color to represent Group. Summarize any trends or interesting features in these two plots.


```{r Q1}
#Multi-Dimensional Scaling
mdsPowerDist<-cmdscale(powerDist,k=2,eig=TRUE)

mdsPowerDist.df<-data.frame(mdsPowerDist$points)%>%
                    dplyr::select(Y1=X1,Y2=X2)

mdsPowerDist.df$Tariff_Group <- rownames(mdsPowerDist.df)

mdsPowerDist.df$Tariff<-rownames(mdsPowerDist.df)%>%word(2)

mdsPowerDist.df$ACornCategory<-word(rownames(mdsPowerDist.df,1))

#Join with AcornInfo
mdsPowerDist.df<-inner_join(x=mdsPowerDist.df,AcornInfo%>%dplyr::select(Acorn,Group,TotalUse),by=c("ACornCategory"="Acorn"))

```

```{r}
p<-mdsPowerDist.df%>%
  ggplot(aes(x=Y1,y=Y2,color=Group,shape=Tariff))+
  geom_point()+
  scale_color_manual(values=c("#66FF33","#FF3333","#CC00CC"))+
  labs(title="Principal Coordinates using pairwise distances of electricity consumption")
  
ggplotly(p)

```

```{r Bubble Plot}
#Total Use as Bubble Size
p<-mdsPowerDist.df%>%
  mutate(TotalUse=round(TotalUse,4))%>%
  ggplot(aes(x=Y1,y=Y2,color=Group,label=ACornCategory))+
  geom_point(shape=1,fill="grey",aes(size=TotalUse))+
  scale_size_continuous(range=c(10,40),trans="exp")+
  labs(title="Bubble Plot")

ggplotly(p)
```
```{r}
colors=AcornInfo$Group

colors[colors=="Affluent"]="Green"
colors[colors=="Comfortable"]="Blue"
colors[colors=="Adversity"]="Red"
colors
symbols(mdsPowerDist$points,circles=AcornInfo$TotalUse,fg=colors,
        main="Principal Coordinates of pairwise distances by Group sized by Total Use")
colors
```


Q2. Create a dendrogram using complete linkage. Plot the dendrogram, labeling the leaves with the category they represent. Cut the dendrogram so four groups are created–show this on the plot. Make a table of these four groups and the three aggregated socio economic groups, and a separate table of the dendrogram groups and electricity tariff types. Are the dendrogram groups associated with either the socio economic group or tariff? Do not perform a test, but summarize any trends in your tables.

```{r}
mod<-hclust(powerDist)
plot(mod,hang=-1,xlab="Group",sub="",labels=as.factor(AcornInfo$Group))
rect.hclust(mod,k=4)


#Cut the dendrogram into k=4 groups
table1<-table(cutree(mod,k=4),AcornInfo$Group)
```

```{r Association with Acorn Group}

table1_melt<-table1%>%
  as.data.frame()%>%
  mutate(Dendrogram_Group =Var1,
         ACornGroup = Var2)

p<-table1_melt%>%
  ggplot(aes(x=Dendrogram_Group,y=Freq,label=Freq))+
  geom_bar(stat="Identity",aes(fill=ACornGroup))+
  coord_flip()+
  labs(title="ACorn group by Dendrogram Group")+
  xlab("Dendrogram Group")+
  ylab("Count")
ggplotly(p)

table2<-table(cutree(mod,k=4),AcornInfo$Tariff)
```


```{r Association with Tariff Group}
table2_melt<-table2%>%
  as.data.frame()%>%
  mutate(Dendrogram_Group=Var1,
         Tariff=Var2)

p<-table2_melt%>%
  ggplot(aes(x=Dendrogram_Group,y=Freq))+
  geom_bar(stat="Identity",aes(fill=Tariff))+
  coord_flip()+
  labs(title="Tariff Group by Dendrogram Group")+
  xlab("Dendrogram Group")+
  ylab("Count")

ggplotly(p)

```

```{r Visualise the Clusters}

Clustered<-mdsPowerDist.df%>%
  inner_join(data.frame(Dendrogram_Group=cutree(mod,k=4),
                        Tariff_Group=names(cutree(mod,k=4))),
             by=c("Tariff_Group"="Tariff_Group"))


options(scipen = 999)
p<-Clustered%>%
  ggplot(aes(x=Y1,y=Y2))+
  geom_point(aes(color=Group,shape=Tariff))+
    scale_color_manual(values=c("#66FF33","#FF3333","#CC00CC"))+
  geom_encircle(aes(group=as.factor(Dendrogram_Group)),color="red",expand=0.02)+
  labs(title="Principal Coordinates with Hierarchical Clustering (Complete linkage, height 4)")

p
```

Q3 In the next two questions we will make a closer examination of the “comfortable” category. We have selected 640 households, 320 with the standard tariff and 320 with the time of use tariff. Note that the profiles (what we want to compare) are in columns 5 to 52. Read in this data from “comfortable.csv.” Do a permanova based on the euclidian distance. What are your conclusions?

```{r}
adonis(comfortable[,5:52]~comfortable$TARIFF,method="euc")
```

Q4 Perform k-means clustering of the profiles from the comfortable households. Make graphs of the within group sum of squares, and the C-H index. Select a number of clusters, referring to featrues of the plots to justify your choice. Create tables of the cluster memberships and the detailed acorn categories, and of the cluster memberships and tariff. Are there any associations? Assess qualitatively; a chi-squared test would be appropriate here, but you need not perform one. 

```{r}
WSS = rep(NA,10)
for (i in 2:11) {
  WSS[i-1] = kmeans(comfortable[,5:52],centers=i,nstart=10)$tot.withinss
}

plot(2:11,WSS,xlab="Number of Clusters")
```

````{r}
BSS = rep(NA, 10)
for (i in 2:11) {
BSS[i-1] = kmeans(comfortable[, 5:52], centers = i, nstart = 10)$betweenss
}
````

```{r Fit K = 2 Means Clustering}
kmod=kmeans(comfortable[,5:52],centers=2,nstart=10)
```

```{r Tariff}
table(comfortable$TARIFF,kmod$cluster)%>%
  as.data.frame()%>%
    dplyr::select(Tariff=Var1,ClusterGroup=Var2,Freq)%>%
  ggplot(aes(x=ClusterGroup,y=Freq,fill=Tariff,label=Freq))+
  geom_bar(stat="identity",position="fill")+
  scale_y_continuous(labels=scales::percent)+
  labs(title="Tariff Representation in Cluster Groups")
```


````{r ACorn}
table(comfortable$ACORN,kmod$cluster)%>%
  as.data.frame()%>%
    dplyr::select(ACORN=Var1,ClusterGroup=Var2,Freq)%>%
  ggplot(aes(x=ClusterGroup,y=Freq,fill=ACORN,label=Freq))+
  geom_bar(stat="identity",position="fill")+
  scale_y_continuous(labels=scales::percent)+
  labs(title="ACorn Category Representation in Cluster Groups")
``` 

```{r}
#Choosing 4 Clusters
kmod4 = kmeans(comfortable[,5:52], centers = 4, nstart = 10)
table(comfortable$ACORN, kmod4$cluster)%>%
  as.data.frame()%>%
    dplyr::select(ACORN=Var1,ClusterGroup=Var2,Freq)%>%
  ggplot(aes(x=ClusterGroup,y=Freq,fill=ACORN,label=Freq))+
  geom_bar(stat="identity",position="fill")+
  scale_y_continuous(labels=scales::percent)+
  labs(title="ACorn Category Representation in Cluster Groups")


table(comfortable$TARIFF, kmod4$cluster)%>%
  as.data.frame()%>%
    dplyr::select(TARIFF=Var1,ClusterGroup=Var2,Freq)%>%
  ggplot(aes(x=ClusterGroup,y=Freq,fill=TARIFF,label=Freq))+
  geom_bar(stat="identity",position="fill")+
  scale_y_continuous(labels=scales::percent)+
  labs(title="Tariff Representation in Cluster Groups")
```


